---
title: "Week4_Project_2"
author: "Ken"
date: "2017-March-14th"
output:
  html_document: default
  pdf_document: default
---

Title:
The report Basic inferential data analysis for ToothGrowth

Author: 
Ken Gu

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Overview:

This report use basic exploratory data analysis to check the ToothData 
The report calculate the following numbers:
mean data for each dose/supp
pvalue and confidence for supp 
pvalue and confidence for dose


```{r}


library(ggplot2)
library(dplyr)
data(ToothGrowth)

```

Step 1: Load the data and plot the data based on the supp


```{r}

head(ToothGrowth)
g1 <- ggplot(ToothGrowth, aes(x=dose, y=len))
g1 + geom_point(aes(colour=supp)) + geom_line(aes(colour=supp))

```

Step 2: Use groupby method to display the mean of each supp/dose

```{r}
grp <- group_by(ToothGrowth, supp,dose)
summary1 <- summarise(grp, meanlen = mean(len) )
summary1
```

Step 3: 

```{r}

# Step 3.1: Compare Supp
test1 <- t.test(ToothGrowth$len ~ ToothGrowth$supp, data = ToothGrowth)
test1$p.value
test1$conf.int

```
Because the p-value is greater than 5%, so it will not be included

```{r}

# Step 3.2: Compare Dose
dose5 <- filter(ToothGrowth, dose==0.5)$len
dose10 <- filter(ToothGrowth, dose==1.0)$len
dose20 <- filter(ToothGrowth, dose==2.0)$len

# Check dose5 and dose10 p-value
pdose5_dose10_test1 <- t.test(dose5, dose10, paired=FALSE, var.equal=TRUE)
pdose5_dose10_test2 <- t.test(dose5, dose10, paired=FALSE, var.equal=FALSE)
pdose5_dose10_test1$p.value
pdose5_dose10_test2$p.value
pdose5_dose10_test1$conf.int
pdose5_dose10_test2$conf.int

pdose10_dose20_test1 <- t.test(dose10, dose20, paired=FALSE, var.equal=TRUE)
pdose10_dose20_test2 <- t.test(dose10, dose20, paired=FALSE, var.equal=FALSE)
pdose10_dose20_test1$p.value
pdose10_dose20_test2$p.value
pdose10_dose20_test1$conf.int
pdose10_dose20_test2$conf.int

pdose5_dose20_test1 <- t.test(dose5, dose20, paired=FALSE, var.equal=TRUE)
pdose5_dose20_test2 <- t.test(dose5, dose20, paired=FALSE, var.equal=FALSE)
pdose5_dose20_test1$p.value
pdose5_dose20_test2$p.value
pdose5_dose20_test1$conf.int
pdose5_dose20_test2$conf.int

```
Because all p-value are less than 5%, so its clearly stated that the dose has a strong impact on the tooth length

Conclusion: 
The above report shows that 'dose's increasement can directly impact tooth growth', while supplement does not have impact.

